Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-04-06 manuscript.tex
add more figures and replace with macros

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
\documentclass[final,3p,times,authoryear]{elsarticle}
% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

@@

\newcommand*{\fe}{\mv{r}}
\DeclareMathOperator{\mypoly}{Poly} % filtered error

\newcommand*{\figSize}{.99}

@@

%% Author affiliation
\affiliation{organization={
  Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST)
},%Department and Organization
            addressline={123 Cheomdangwagi-ro, Buk-gu}, 
            city={Gwangju},
            postcode={61005}, 
            state={},
            country={Korea}}

@@

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in[1,\cdots,n],j\in[1,\cdots ,m]
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\text{col}_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
\end{itemize}

@@

Consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
    =
    \mysat(\mv\tau)
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\mv\tau)}\le \bar\tau$, where $\bar\tau$ denotes the maximum norm of control input.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
We introduce the following properties:
\begin{prop} 
    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
    \label{prop:M}
\end{prop}

\begin{prop} 
    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
    \label{prop:skew}
\end{prop}

\begin{prop}
    The disturbance $\mv\tau_d$ is bounded so that $\norm{\mv\tau_d}\le \bar\tau_d$.
    \label{prop:dis_bound}
\end{prop}

@@

Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
\begin{equation}
    \mm M \dot\fe
    =
    -\mm V_m \fe
    -\mm K \fe
    + \mv f
    -\mv \tau_d + \mysat(\mv\tau)
    ,
    \label{eq:sys:filtered}
\end{equation}
where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
    =
    \mm K \fe
    +\mm M(-\ddqd+\mm\Lambda\dot{\mv e})
    +
    \mm V_m(-\dqd+\mm\Lambda\mv e)
    -
    \mm F
    -
    \mm G
    \in\R^n
$ denotes the lumped system uncertainty.

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \mm M (
            -\mm V_m \fe -\mm K \fe + \mv f
            -\mv \tau_d + \mysat(\mv\tau)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\mm M}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\mv\tau)
            -\mv \tau_d
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\mv \tau))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\mv\tau)-\mv\tau^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.

To overcome this issue, a DNN is employed to approximate $\mv\tau^*$.
Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.

In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
\begin{align}
    \mv\tau^*=& \idealNN+\mv\epsilon,
    \label{eq:control:ideal}
\end{align}
which is estimated online by
\begin{align}
    \mv\tau =& \estNN,
    \label{eq:control:est}
\end{align}
where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.

Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $\mathcal V_1$ can be rewritten as
\begin{equation}
    \dot{\mathcal V}_1
    \le 
    -\lambda_{\min}(\mm K)\norm{\fe}^2
    +
    \bar\tau_d\norm{\fe}
    +
    \fe^\top (\mysat(\hat\NN)-\idealNN-\mv\epsilon)
    .
    \label{eq:lya1:dot2}
\end{equation}
Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).

@@

The DNN architecture $\NN(\q_{NN};\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \NN_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top \q_{NN},
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\mv\tau$ (\ie $l_{k+1}=n$).

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
\begin{equation}
    \wth := 
    \begin{bmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{bmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
        &
        i=k 
        \\
        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
        & 
        i=k-1
        \\
        &
        \vdots 
        \\
        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
        &
        i = 0
    \end{cases},
    \label{eq:NN:grad}
\end{equation}
where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

The control objective can be represented as follows:
\begin{equation}
    \begin{matrix}
        \min_{\estwth} \ J(\fe;\estwth):= 
        \tfrac{1}{2} \fe^\top  \mm W\fe
        \\ \\
        \begin{aligned}
        \text{s.t. }&c_{j}(\estwth) 
        \le0, \quad j\in\mathcal{I},
        \end{aligned}
    \end{matrix}
    \label{eq:opt:problem1}
\end{equation}
where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top  \mm W\fe$ is the objective function, and $\mm W\in\R^{n\times n}$ is a symmetric positive weighting matrix.
Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints. 
Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
\begin{equation}
    L(
        \fe,\estwth,[\lambda_j]_{j\in\mathcal I}
    ) 
    := 
    J(\fe;\estwth) 
    + 
    \sum_{j\in\mathcal I}
    \lambda_{j}
    c_{j}(\estwth)
    \label{eq:lagrangian}
\end{equation}
where $\lambda_j$ denotes the Lagrange multiplier for each constraint.

The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\alpha \pptfrac{L}{\estwth}
            =
            -\alpha 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j\pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad \forall j\in\mathcal I,
        \label{eq:adap:lbd}
            \\
            \lambda_j & = \max(\lambda_j,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}
\end{subequations}
where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity. 
The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive. When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation. Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero. Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.

At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\partial L/\partial \estwth=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
% The KKT condition is satisfied, when $\estwth$ converges to $\idealwth$, since $\partial L/\partial \estwth=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).

@@

Since $\mv\tau = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
\begin{equation}\label{eq:linear:map}
    \begin{aligned}
    \mv\tau 
    = 
    &
    \estNN 
    % = 
    % \myvec(\estNN)
    =
    \myvec(
        \estwV_k^\top \estact_k
    ) 
    = 
    (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top
    \myvec(\estwV_k)
    \\
    = &
    \underbrace{
        (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top}_{:=\mm T(\estact_k)}
    \estwth_k 
    =
    \mm T(\estact_k) \estwth_k.
    \end{aligned}
\end{equation}
Therefore, the convexity of the input constraints in $\mv\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.

>>>>

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
% \documentclass[final,3p,times,authoryear]{elsarticle}
% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
% \documentclass[final,5p,times,authoryear]{elsarticle}
\documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

@@

\newcommand*{\figSizeTwoCol}{.49}
\newcommand*{\figSizeOneCol}{0.98}

@@

%% Author affiliation
\affiliation{organization={
  Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST)
},%Department and Organization
            addressline={123 Cheomdangwagi-ro, Buk-gu}, 
            city={Gwangju},
            postcode={61005}, 
            % state={},
            country={Korea}}

@@

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in[1,\cdots,n],j\in[1,\cdots ,m]
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
\end{itemize}

@@

Consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \rbM\ddq + \rbVm + \rbF + \rbG + \rbd
    =
    \mysat(\rbu)
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents disturbance and $\rbu\in\R^n$ denotes the control input. 
The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$ and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \bar\tau$, where $\bar\tau$ denotes the maximum norm of control input.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
We introduce the following properties:
\begin{prop} 
    The inertia matrix $\rbM$ is symmetric, positive definite and bounded.
    \label{prop:M}
\end{prop}

\begin{prop} 
    The Coriolis/centripetal matrix $\rbVm$ can always be selected so that the matrix $(\dot{\rbM}-2\rbVm)$ is skew-symmetric.
    \label{prop:skew}
\end{prop}

\begin{prop}
    The disturbance $\rbd$ is bounded so that $\norm{\rbd}\le \bar\tau_d$.
    \label{prop:dis_bound}
\end{prop}

@@

Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
\begin{equation}
    \rbM \dot\fe
    =
    -\rbVm \fe
    -\mm K \fe
    + \mv f
    -\rbd + \mysat(\rbu)
    ,
    \label{eq:sys:filtered}
\end{equation}
where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
    =
    \mm K \fe
    +\rbM(-\ddqd+\mm\Lambda\dot{\mv e})
    +
    \rbVm(-\dqd+\mm\Lambda\mv e)
    -
    \rbF
    -
    \rbG
    \in\R^n
$ denotes the lumped system uncertainty.

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \rbM (
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\rbu)
            -\rbd
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\rbu)-\rbu^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.

To overcome this issue, a DNN is employed to approximate $\rbu^*$.
Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.

In conclusion, the ideal control law $\rbu^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
\begin{align}
    \rbu^*=& \idealNN+\mv\epsilon,
    \label{eq:control:ideal}
\end{align}
which is estimated online by
\begin{align}
    \rbu =& \estNN,
    \label{eq:control:est}
\end{align}
where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.

Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $V_1$ can be rewritten as
\begin{equation}
    \ddtt{V}_1
    \le 
    -\lambda_{\min}(\mm K)\norm{\fe}^2
    +
    \bar\tau_d\norm{\fe}
    +
    \fe^\top (\mysat(\hat\NN)-\idealNN-\mv\epsilon)
    .
    \label{eq:lya1:dot2}
\end{equation}
Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).

@@

The DNN architecture $\NN(\q_{NN};\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \NN_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top \q_{NN},
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
\begin{equation}
    \wth := 
    \begin{bmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{bmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
        &
        i=k,
        \\
        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
        & 
        i=k-1,
        \\
        &
        \vdots 
        \\
        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
        &
        i = 0,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

The control objective can be represented as follows:
\begin{equation}
    \begin{matrix}
        \min_{\estwth} \ J(\fe;\estwth):= 
        \tfrac{1}{2} \fe^\top \fe
        \\ \\
        \begin{aligned}
        \text{s.t. }&c_{j}(\estwth) 
        \le0, \quad j\in\mathcal{I},
        \end{aligned}
    \end{matrix}
    \label{eq:opt:problem1}
\end{equation}
where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top \fe$ is the objective function.
Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints. 
Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
\begin{equation}
    L(
        \fe,\estwth,[\lambda_j]_{j\in\mathcal I}
    ) 
    := 
    J(\fe;\estwth) 
    + 
    \sum_{j\in\mathcal I}
    \lambda_{j}
    c_{j}(\estwth)
    ,
    \label{eq:lagrangian}
\end{equation}
where $\lambda_j$ denotes the Lagrange multiplier for each constraint.

The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\alpha \pptfrac{L}{\estwth}
            =
            -\alpha 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j\pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad \forall j\in\mathcal I,
        \label{eq:adap:lbd}
            \\
            \lambda_j & = \max(\lambda_j,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}
\end{subequations}
where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity. 
The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive. When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation. Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero. Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.

At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\pptfrac{L}{\estwth}=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
% The KKT condition is satisfied, when $\estwth$ converges to $\idealwth$, since $\partial L/\partial \estwth=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).

@@

Since $\rbu = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\rbu$ can be derived: 
\begin{equation}\label{eq:linear:map}
    \begin{aligned}
    \rbu 
    = 
    &
    \estNN 
    % = 
    % \myvec(\estNN)
    =
    \myvec(
        \estwV_k^\top \estact_k
    ) 
    = 
    (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top
    \myvec(\estwV_k)
    \\
    = &
    \underbrace{
        (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top}_{:=\mm T(\estact_k)}
    \estwth_k 
    =
    \mm T(\estact_k) \estwth_k.
    \end{aligned}
\end{equation}
Therefore, the convexity of the input constraints in $\rbu$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
